

#Peer Assesment 1

##Code for rxeading in the dataset and/or processing the data

###Code for reading in the dataset
```{r, echo=TRUE}
data<-read.csv("activity.csv")
as.data.frame(data)
```

###Process/transform the data (if necessary) into a format suitable for your analysis
```{r, echo=TRUE}
library(plyr)
library(dplyr)

ddply(data, .(date), summarize,  steps=sum(steps))

data2<- ddply(data, .(date), summarize,  steps=sum(steps,na.rm = TRUE))
```
##Histogram of the total number of steps taken each day
```{r,echo=TRUE}
hist(data2$steps, col ="red",main ="Number_of_Steps",xlab="Steps_per_day",ylim=c(0,30))
```

##Mean and median number of steps taken each day
```{r, echo=TRUE}
mean(data2$steps, na.rm = TRUE)

median(data2$steps, na.rm = TRUE)
```
##Time series plot of the average number of steps taken
```{r,echo=TRUE}
data3<- ddply(data, .(interval), summarize,  steps=mean(steps,na.rm = TRUE))

plot(data3$interval, data3$steps,type="l", main="Average number of steps", xlab = "Intervals", ylab = "Average numberof steps") 
```

##The 5-minute interval that, on average, contains the maximum number of steps
```{r, echo=TRUE}
data3[which.max(data3$steps),1]
```
##Code to describe and show a strategy for imputing missing data

####Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NA)
```{r, echo=TRUE}
complete<-data[complete.cases(data),]
    
NArows<- nrow(data)-nrow(complete)
```
####Devise a strategy for filling in all of the missing values in the dataset. 
```{r, echo=TRUE}
miss<-data[!complete.cases(data),]
```
- adding column with interval as replacing values for NA and then select all columns but the NAs, i.e only columns 4,2,3
```{r, echo=TRUE}
miss2=left_join(miss,data3,'interval') 

miss3<- miss2[,c(4,2,3)]
colnames(miss3) <- c("steps","date", "interval")
```
- integrate the complete data with the replaced missing values
```{r, echo=TRUE}
data4<- rbind(miss3,complete)
```
##Histogram of the total number of steps taken each day after missing values are imputed
```{r,echo=TRUE}
data5<- ddply(data4, .(date), summarize,  steps=sum(steps))
hist(data5$steps, col ="red",main ="Number of Steps",xlab="Steps per day",ylim=c(0,40))  
```
##Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

###Create a new factor variable in the dataset with two levels - "weekday" and "weekend" indicating whether a given date is a weekday or weekend day.
```{r, echo=TRUE}
weekday<-weekdays(as.Date(data5$date))
weekday2<-ifelse(weekday=="s?bado"|weekday=="domingo","weekend","weekday")
```
###Make a panel plot containing a time series plot
```{r,echo=TRUE}
a<-as.data.frame(weekday)
b<-as.data.frame(weekday2)
c<-as.data.frame(data5$date)
data6<-cbind(a,b,c)
colnames(data6) <- c("weekday","daytype", "date")

data7=left_join(data4,data6,'date') 

data8<- ddply(data7, .(interval,daytype), summarize,  steps=mean(steps))
require(lattice)
xyplot(steps ~ interval | daytype, data = data8, type = "l", layout = c(1, 2), main="Average number of steps", xlab = "Intervals", ylab = "Average numberof steps")
```

